---
title: "Templates_GitHubPages"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: true
      smooth_scroll: true
    theme: lumen
    highlight: tango
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: 0;
  margin-right: auto;
}
blockquote {
    padding: 10px 20px;
    margin: 0 0 20px;
    font-size: 14px;
    border-left: 5px solid #eee;
}

h1.title {
  font-size: 38px;
  color: #000000;
  }
  
h1 { /* Header 1 */
  font-size: 28px;
  color: #0033cc;
}
h2 { /* Header 2 */
    font-size: 28px;
	color: #0099ff
}
h3 { /* Header 3 */
    font-size: 14px;
	color: #6600cc
}
</style>
```{r, echo=FALSE}

htmltools::img(src = knitr::image_uri(file.path("./KtZuerichLogo.png")),
               alt = 'logo', 
               style = 'position:absolute; top:0; right:0; padding:0px;')
```

# R setup
```{r setup, echo=T, results='hide', message=FALSE, warning=FALSE}
# Import libraries
library(tidyverse) # collection of R packages designed for data science

# Number formatting
options(scipen = 1000000)
options(digits = 6)
```

# How to add an iframe

>knitr::include_url("https://www.web.statistik.zh.ch/cms_vis/Allgemeines_D3_VorlageKarte/", height = "800px")

```{r, echo = FALSE}

knitr::include_url("https://www.web.statistik.zh.ch/cms_vis/Jugendstrafrechtspflege_ZuF/verurteilungenDelikte.html", height = "620px")

```

# How not to print code

>{r, echo = FALSE}

```{r, echo = FALSE}

```

# How to avoid printing warnings and messages of code

>{r, collapse=TRUE, warning=FALSE,  message=FALSE}

```{r, collapse=TRUE, warning=FALSE,  message=FALSE}

```
